Machine Learning Models for the Segmentation of e-Coaching Text (summarizes the hypothesis of the paper)

### 2018-02-26 paper-amia-2018/manuscript.tex
prepared the layout of the paper

\title{Machine Learning Models for Text Segmentation}

@@

@@

@@

\subsection*{\textit{Prediction method}}
Generally, a sequence can be viewed as a temporally ordered set of events. In this study, an event is a behavior code that also has a symbolic representation.

@@

\section*{Results}
Experimental evaluation of the proposed method is conducted on both under and over-sampled sequences. Predictive performance summary of the proposed methods on under and over-sampled sequences is presented in Table.

@@

\section*{Conclusion}
In this paper, we compared the accuracy of Recurrent Neural Networks with Markov Chain and Hidden Markov Model for the task of predicting the success of motivational interviews. We found out
that individual patient-provider communication exchanges

>>>>

\title{Machine Learning Models for the Segmentation of e-Coaching Text (summarizes the hypothesis of the paper)}

@@

1) Motivation: Why do we care about the problem and the results? \\
2) Problem statement: What problem is the paper trying to solve and what is the scope of the work? \\
3) Approach: What was done to solve the problem? \\
4) Results: What is the answer to the problem? \\
5) Conclusions: What implications does the answer imply?

@@

What is the problem? \\

Why is the problem important? \\

What has so far been done on the  problem?\\
1) describes previous work in more technical detail \\
2) as far as needed for a proper understanding of the contribution of the paper \\

What is the contribution of the paper on the problem?\\
1) What are the rival approaches? \\
2) What are the drawbacks of each?\\
3) How has the battle between different approaches progressed?\\
4) What are the major outstanding problems? (This is where you come in)\\

Is the contribution original? Explain why \\

Is the contribution non-trivial? Explain why \\

The authors are not aware of any other work where this approach has been considered.

@@

Part 1

1) What algorithms or data structures did you select? Who created them? What is their asymptotic behavior? What other specific characteristics are worth noting for this study?\\
2) What programming language and platform did you use? What impact did these choices have on your project?\\

Part 2

1) How specifically did you implement the algorithms?\\
2) How did you handle instrumentation code? Why?\\
3) Did you perform any optimizations? Why or why not?\\
4) How did you choose to test and benchmark your code?\\
5) What inputs (data) did you select to test your implementations? Why?\\

\subsection*{\textit{Segmentation method}}
Generally, a sequence can be viewed as a temporally ordered set of events. In this study, an event is a behavior code that also has a symbolic representation.

\textbf{Naive Bayes}: comming soon...

\textbf{Support Vector Machine}: comming soon...

\textbf{K-Nearest Neighbour}: comming soon...

\textbf{Recurrent Neural Networks}: comming soon...

@@

\section*{Results}
Experimental evaluation of the proposed method is conducted on both under and over-sampled sequences. Predictive performance summary of the proposed methods on under and over-sampled sequences is presented in Table.\\

1) In general, the pure, unbiased results should be presented first without interpretation (van Wagenen 1990). \\
2) These results should present the raw data
or the results after applying the techniques outlined in the methods section. The results are simply results; they do not draw conclusions.

\begin{table}[ht]
\centering
\caption{Performance of MC, HMM, and RNN for predicting the success of under and over-sampled patient-provider communication sequences. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_under_over_sampled}
  \begin{tabular}{|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{lexical features only}} & \multicolumn{3}{|c|}{\textbf{lexical features + topics}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score}\\ \hline

 Naive Bayes Multinomial & 0.7060 & 0.7044 & 0.7038 & 0.7932 & 0.7799 & 0.7775 \\ \hline
 Support Vector Machine & 0.6395 & 0.6385 & 0.6379 & 0.7111 & 0.7029 & 0.7000\\ \hline
 K-Nearest Neighbour & 0.6244 & 0.6143 & 0.6067 & 0.7775 & 0.7567 & 0.7520\\ \hline
 Long Short Term Memory & \textbf{0.8733} & \textbf{0.8681} & \textbf{0.8677} & \textbf{0.8424} & \textbf{0.8385} & \textbf{0.8381}\\ \hline
 Gated Recurrent Unit & 0.8705 & 0.8676 & 0.8673 & 0.8412 & 0.8377 & 0.8373\\ \hline 
  \end{tabular}
\end{table}

Predictive performance summary of the proposed methods on under and over-sampled sequences is presented in Table.\\

\begin{table}[ht]
\centering
\caption{Performance of MC, HMM, and RNN for predicting the success of under and over-sampled patient-provider communication sequences. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_under_over_sampled}
  \begin{tabular}{|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{lexical features only}} & \multicolumn{3}{|c|}{\textbf{lexical features + topics}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Score}\\ \hline

 Naive Bayes Multinomial & 0.7060 & 0.7044 & 0.7038 & 0.7932 & 0.7799 & 0.7775 \\ \hline
 Support Vector Machine & 0.6395 & 0.6385 & 0.6379 & 0.7111 & 0.7029 & 0.7000\\ \hline
 K-Nearest Neighbour & 0.6244 & 0.6143 & 0.6067 & 0.7775 & 0.7567 & 0.7520\\ \hline
 Long Short Term Memory & \textbf{0.8733} & \textbf{0.8681} & \textbf{0.8677} & \textbf{0.8424} & \textbf{0.8385} & \textbf{0.8381}\\ \hline
 Gated Recurrent Unit & 0.8705 & 0.8676 & 0.8673 & 0.8412 & 0.8377 & 0.8373\\ \hline 
  \end{tabular}
\end{table}

We took the inspiration for the representation of behavior codes from the idea of word embeddings. Word embedding is a representation of words in
low-dimensional space by vectors, which contain the features of the words. In our study, we employed embedding in place of one-hot vectors for representation of behavior codes as input to LSTM and
GRU, since one-hot vectors are high-dimensional and sparse.

\begin{figure}[!htb]
    \centering
    \includegraphics[width=0.90\textwidth]{figures/roc-curves.png}
    \caption{\textbf{ROC curves compared the performance of different models}.}
    \label{fig:roc-curves}
\end{figure}

@@

1) What, specifically, did you learn from comparing these algorithms or data structures? \\
2) What do your results say about the problem or question you were investigating?\\
3) Was your hypothesis confirmed or disproved?\\
4) Are the results what you expected?\\
5) If you obtained anomalies or other unexpected results, can you explain them? If not, how could you set about in the future to identify what caused them? \\
6) How do your results compare to past findings? Are they consistent? Different?Why? \\
7) How would you respond to objections or questions that other researchers might have about your methods, results, or interpretations? \\
8) What is new and significant?\\

\section*{Conclusion}
In this paper, we compared the performance of machine learning models for the task of segmentation of e-coaching text. We found out that k-nearest neighbour provides the best performance for the segmentaion of text in terms of all performance metrics. Manual segmentation of e-coaching data is very resource-intensive and time consuming task, which can significantly decrease the time and effort required to develop effective behavioral interventions. Our
proposed methods can help to identify individual text segments, which can be annotated directly with a classification model and increase
the effectiveness of behavioral interventions.

1) The hypothesis and the evidence for and against it are briefly restated \\
2) The original motivation is recapitulated \\
3) The state of the field in the light of this new contribution is reassessed \\
4) describes future research and new directions suggested by the contribution\\
5) in particular, research that would improve the evidence for or against the hypothesis
